Supplementary Materials

### 2018-03-28 paper/intro.tex
update intro

In summary, the key contributions of the proposed works are the following:
\begin{itemize}
  % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
    \item Introduce the perturbation-driven exploration paradigm for exploring natural language processing models;

    \item Perform error analysis by examining the stability of the predictions under perturbation;

    \item Enhance the visual encoding of the attention by overlaying sentence linguistic structure to allow grammar-guided simplification;

    \item Enable the interrogation of the relationships among input sentences, model internals, and the prediction by interactively exploring how the change in one place affects other parts of the model.
\end{itemize}
%
% In addition,

>>>>

In summary, the key contributions of the proposed works are the following:
\begin{itemize}
  % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
    \item Distill the perturbation-driven exploration paradigm from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;

    \item Present the NLIZE system that enriches such a paradigm by providing an intuitive environment where the domain experts can readily express experiment ideas and obtain instantaneous feedbacks; 
    %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
    %\item Perform error analysis by examining the stability of the predictions under perturbation;

    \item Introduce an optimization scheme for correcting a failed prediction based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network.
    % to minimally update the model to fix a failed prediction, which help reason about the  better understand the re the question about how t

    \item Enhance the visual encoding of the attention by imposing sentence linguistic structure to allow grammar-guided sentence simplification.
\end{itemize}
%
% In addition,

### 2018-03-28 paper/task.tex
update intro

During our long-term collaboration with NLP experts, we have conducted extensive discussion to understand the common approach employed by researcher for assessing the behavior of a model.%
The prediction accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model, however, the accuracy number alone does not provide the full story.
For example, the model may produce correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that can not be generalized in real word scenarios).
%
As a result, the domain experts often rely on exploration centric approach to conduct error analysis and obtain intuition.

There is little one can learn when everything is behaving as expect, therefore,
observing how model make mistakes under various scenarios is at the center of such a process.
The experts often start with simple failure examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction. This exercise help isolate where in the input is likely contributed to the failures. For many NLP models, the attention information (see Section~\ref{sec:attention}) is essential to infer the mechanism of the model. The expert can print out the attention values or generate plots to visualize the alignment between sentences or compare attentions. As the experts explore more variation of similar examples, combined with their domain knowledge, he / she may develop hypotheses about the cause of failures, or ask additional questions, which lead to further experimentation.
%
The requirement for such exploratory analysis meshed nicely with the benefit of interactive visual exploration, in which the user can make adjustment on-the-fly and obtain instantaneous visual feedbacks that encode various model information.
%
Moreover, by introducing new visual encoding and summarization, we can drastically expand the ways domain experts interact with the model, enable exploration options that is not possible before either due to tedious manual operation or lack of communication channels.

%Through many rounds of discussions with NLP experts,
In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
%
Here, we solidify the visualization tasks to facilitate the exploratory workflow and thought process of the domain experts.
%
\begin{itemize}
    \item Firstly, understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis. It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{T1}).

    %Understand how attention affect the prediction.
    \item Secondly, study the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
    %Study the relationship between model stages (encoder, attention, classifier) and the prediction

>>>>

During our long-term collaboration with NLP experts, we have conducted extensive discussion to understand the common approach employed by researcher for assessing the behavior of a model.%
The prediction accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model, however, the accuracy number alone does not provide the full story.
For example, the model may produce correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that can not be generalized in real word scenarios).
%
As a result, the domain experts also rely on exploration centric approach to conduct error analysis and obtain intuition.

There is little one can learn when everything is behaving as expect, therefore,
observing how model make mistakes under various scenarios is at the center of such a process.
The experts often start with simple failure examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction. This exercise help isolate where in the input is likely contributed to the failures. For many NLP models, the attention information (see Section~\ref{sec:attention}) is essential to infer the mechanism of the model. The expert often print out the attention values or generate plots to visualize sentence alignment or compare attention values. As the experts explore more variation of similar examples, combined with their domain knowledge, he / she may develop hypotheses about the cause of failures, or ask additional questions, which lead to further experimentation.

In such an exploration workflow, NLP researchers often need to utilize multiple scripts and manually run all the experiments. The batch process based approach, is not only time consuming, but also hinders the flow of reasoning which rely on obtaining instantaneous feedbacks, and making many on-the-fly adjustments.
%
Therefore, the expert driven exploration process can greatly benefit from the introduction of an interactive visual exploration environment, where the researchers can easily express their experiment ideas and obtain quick visual feedback of the results.
%
Moreover, by introducing new visual encoding and summarization, we can drastically expand the ways domain experts interact with the model, enable exploration options that is not possible before either due to tedious manual operation or lack of communication channels.

%Through many rounds of discussions with NLP experts,
%In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
%
To support the visual exploratory workflow, we have summarized the following visualization tasks.
%
\begin{itemize}
    \item Firstly, we need to design visual representation for the key information the domain experts are interested in, e.g., input sentences, the attention information, prediction results, the overall model pipeline (T1).
    \item Secondly understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis. It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input
     (\textbf{T1}).

    %Understand how attention affect the prediction.
    \item Secondly, the user should be able to easily express the perturbation of input sentences, the   the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
    %Study the relationship between model stages (encoder, attention, classifier) and the prediction
